---
title: "Classwork 2"
author: Aarushi Sahejpal
date: 05/19/21
output:
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(dplyr)

V <- c("Bears", "Lions", "Dolphins", "Eagles", "Bengals")
```

# 1) Why is the vector shown above an atomic vector? (Explain using two or three sentences)

Because atomic vectors are homogenous, and they are all of the same type. The vector above displays all animals. 

# 2) Use and show R code that will extract "Dolphins" from the vector shown above.
```{r}
V[3]
```

# 3) Use and show R COde that will extract "Bears", "Dolphins" and "Bengals" from the vector shown above.
```{r}
V[c(1,3,5)]
```

# 4) Use and show two Rcoding methods that will show all objects of the vector given above except "Bears".
```{r}
V[V!="Bears"]
V[!is.na("Bears")]

K <- list( x = 3:7, "never", 43, y = list(10,20,30))
```

# 5) Why is the vector given above called a list? (Explain in two or three sentences) If the vector is a list, identify the type of each object in the list.

Lists contain a mixture of objects, and is heterogenous. The vector above is called a list because it contains different types of objects.

# 6) Use and show R code that will give the length of the vector shown above.
```{r}
K <- c( x = 3:7, "never", 43, y = list(10,20,30))
length(c( x = 3:7, "never", 43, y = list(10,20,30)))

# 7) Use and show R code that will output the fourth object in the vector shown above.

K[c(4)]
```
# 8) Use and show R code that will show all objects in the vector (list) given above.
```{r}
K <- list( x = 3:7, "never", 43, y = list(10,20,30))
K
```
# 9) Copy paste and run the tribble given below
```{r}
tribble( ~x,    ~y,    ~w,    ~z,
              210,   300,   220,   180,
              102,   100,   119,   187,
              176,   175,   188,   173,
              87,    95,   91,     94,
              202,   210,  234,    218,
              110,   122,  131,    128,
) -> dt
dt

# 9a) Use and show a map function to find the mean of each column of the dt data table

map_dbl(dt, mean)

# 9b) Use and show a map function to find the standard deviation of each column of the dt data table.

map_dbl(dt, sd)

# 9c) Use and show a map function that will calculate the square root of each value of each column of the data table dt.

dt %>% 
map (sqrt)

# 9d) Use R code to find the mean, max, 1st Quartile, 2nd Quartile, Median, and Mean for each column of the dt data table. (Hint: You do not have to use a map function)

summary(dt)


# 10) 
x <- list(26, 32, 45, 50, 65, 77, 82)
y <- list(30, 43, 50, 58, 62, 71, 88)

# For the lists given above, show and use R code (a map function) to iteratively find:
# a) sums across the two vectors. (Use two methods)

pmap_dbl(list(x,y), sum)

pmap_dbl(list(x,y), function(first, second) (first + second)/2)

# b) the calculation of the square of the x value minus the square root of the y value.

map2(x,y,~sqrt(.x)-sqrt(.y))

# c) the ratio of the common log of the x value to the natural log of the y value.

map2_dbl(x,y, ~log(.x) + log(.y))
```



